Tor's Usability for Censorship Circumvention

### 2016-04-05 pets2017-paper/pets2017-paper.tex
finish up qualitative results section

\subsubsection{Results} 
{\color {red} meta couple-sentence summary of the feeling we get from the experiment. All quotes are paraphrase from a live transcription.}\\

@@

None of the participants who attempted to configure a proxy were successful. Many of the participants followed the directions in the interface to look at the Internet settings in another browser to see whether it is configure to use a local proxy, but they never found the proxy information since none of the other browsers had the information. What further frustrated the situation was that the other browsers did not explicitly state that no proxy was configured, which caused many of our participants to search for proxy settings.

%proxies
\begin{quotation}
\noindent P15:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did.''}
\end{quotation}

Providing participants with feedback about taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc. can prevent participants from unnecessarily configuring a proxy and to connect successfully. \\

\noindent{\bfseries Sources of Frustration} 
%time
\begin{quotation}
\noindent P16:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\

\noindent P6:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}\\

\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, of if it was just slow.''}\\
\end{quotation}

%lack of knowledge 
\begin{quotation}
\noindent P2:\textit{"I don't know what any of those means (list of bridges), I don't know what that (proxy)
 means at all."}\\

@@

 \noindent P4:\textit{``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean for me?''}\\

 \noindent P16:\textit{``Because I never configured a proxy or worked with that stuff, I was just going to keep clicking and pray.''}
\end{quotation}

@@

\section{Quantitative Analyses of the Interfaces (Study 2)}
We performed quantitative research to quantify the existing problems
and the impact of our redesign by generating numerical data to transform
into usable statistics. Specifically, we collected all events, transitions, 
and state for Tor Browser 5.0.3 and the redesigned Tor Browser. Participant
logs of how they interacted with each of these interfaces are used to both
quantify the issues we encountered in our previous qualitative 
study and to examine the differences in success rate, time to completion,
and configuration choices between the two versions.

>>>>

\subsubsection{Results} 
In this section, we discuss problems encountered by our participants at each step of the configuration process and solutions to those problems. We conclude with our goals for improving the configuration interface. Because of the small sample size of qualitative studies, we can only state that these are problems that participants can encounter when configuring. We confirm the statistical significance of some of the problems in our quantitative study (section ~\ref {sec:quantitative}. All quotes are paraphrased from live transcriptions of participant interviews.\\

@@

None of the participants who attempted to configure a proxy were successful. Many of the participants followed the directions in the interface to look at the Internet settings in another browser to see whether it is configure to use a local proxy, but they never found the proxy information since none of the other browsers had the information. What further frustrated the situation was that the other browsers did not explicitly state that no proxy was configured, which caused many of our participants to search for proxy settings.\\

\noindent{\bfseries Progress Bar} 
Users were generally displeased with the lack of feedback on the progress bar. The process seemed to take too long for them, even in the ideal case in which a user chose the correct configuration in the first attempt. If users chose particular wrong configurations (i.e. a syntactically valid but nonfunctional proxy), they would be waiting for an indefinite period of time, because there is no timeout.

\begin{quotation}
\noindent P16:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\

\noindent P6:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}
\end{quotation}

As a technical artifact of how the progress bar is implemented, the progress bar remains empty on subsequent attempts to connect to the Tor Network until the percent progress supersedes the last displayed progress value (i.e. a participant who saw 30\% progress on their first attempt would see 0\% progress in the progress bar until subsequent attempts got at least 40\% progress). The negative feedback of a 0\% progress bar would cause users to assume that their subsequent attempts were wrong, even if they were correct. 
\begin{quotation}
\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, of if it was just slow.''}
\end{quotation}

Ensuring that the progress bar faithfully displays the current status can encourage users to wait for correct configurations to successfully connect to the Tor network.

\begin{quotation}
\noindent P15:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did.''}
\end{quotation}

Providing participants with feedback about taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc. can prevent participants from unnecessarily configuring a proxy and to connect successfully.\\

\noindent{\bfseries User Communication Failure} Many participants, including participants who were pre-screened for high technical ability and previous experience with using Tor, were not familiar with the vocabulary. 
\begin{quotation}
\noindent P2:\textit{"I don't know what any of those means (list of bridges),or what that (proxy)
 means at all."}\\

@@

 \noindent P4:\textit{``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean?''}\\

 \noindent P16:\textit{``Because I never configured a proxy or worked with that stuff, I was just going to keep clicking and pray.''}
\end{quotation} 
In addition to the text being not as helpful as it would have been had users been able to understand, this discouraged our users during the process.\\

\noindent{\bfseries Final Thoughts}
We believe that the interface is too technical for users to understand and overburdens users with tasks. From our observations in this qualitative study, our goal in redesigning the interface was to making the vocabulary more accessible to the average user, requiring the user to make fewer decisions, and automating parts of configuration that don't increase risk to high-risk users.

@@

\section{Quantitative Analyses of the Interfaces (Study 2)}
\label{sec:quantitative}
We performed quantitative research to quantify the existing problems
and the impact of our redesign by generating numerical data to transform
into usable statistics. Specifically, we collected all events, transitions, 
and state for Tor Browser 5.0.3 and the redesigned Tor Browser. Participant
logs of how they interacted with each of these interfaces are used to both
quantify the issues we encountered in our previous qualitative 
study and to examine the differences in success rate, time to completion,
and configuration choices between the two versions.
